Fitness Cost

### 2022-01-18 graphs_newt_snakes/fitness_cost.Rmd
I have started to run slim scripts to find a good value for the fitness cost. I have updated the 1on1 scripts to run better (like reducing the phenotype caculations, and including the files that need to be written out

If a phenotype of 3 is half the total fitness the cost wold be log 2

@@

>>>>

If a phenotype of 3 is half the total fitness the cost would be log 2

@@

## Extra thoughts

Right now the phenotype of newts and snakes goes down due to fitness cost. However, it does not go down to 0. Which might indicate that there is a benefit for having a costly phenotype. I think the cost is too high in this case.

Original choice is 10 phenotypes dropped to ~0.3
Next choice is 100 phenotypes hold around 2-3

what would phenotypes be like for 10, 20, 30, 40, 50, 60, 70, 80, 90, and 100
